\documentclass[10 pm]{article}


\title  {CSD4301 Section 1 - Assignment 3 - The PIM DB Use Cases and UML Agile Design Document }


\begin{document}
\maketitle
\author{}

\section * {Team members}

\textsc{Jai rino lumi C0738738}\\
\textsc{Rajdeep Kaur C0739309}\\
\textsc{Sandeep Kaur Kanda C0740033}\\
\textsc{Manpreet Kaur C0736236}\\
\textsc{Beant Kaur C0731867}\\

\section * {Use Case:}

\section * {Assess Employee Performance}
\subsection {GOAL}
To enable the HR Manager to assess the performance of employees throughout the Project
\subsection {Actors}
Hr Managers who performs hiring,  employees performance assessment and termination
\subsection {Scenario}

\begin{enumerate}
\item Step 1. The system shall provide the HR Manager with a UI PANEL that allows selection of an employee 
and text area to type in feedback for the employee.
\item Step 2. The system shall provide the HR Manager with the screen to view the previous performance rating history.
\item Step 3. The system shall provide the candidate with a screen to view the performance rating given.
\item Step 4. The system shall provide the HR Manager a confirmation email when the rating is accepted.
\item Step 5. The system shall provide the candidate with a screen that allows to fill out the survey forms about the process.
\end{enumerate}

\subsection{Alternate Flows}
\begin{enumerate}
\item Step 1.  The system shall provide the candidate with a option to decline the rating given
 and text area to type the reason for rejection.
\item Step 2. The system shall schedule meeting with manager for discussion.
\item Step 3. The use case ends.
\end{enumerate}

\section * {UML:}

\section *{Web Application}
\subsection{Data members}
\begin{enumerate}
\item Employeename String
\item Ratinglevel String
\item Date date
\end{enumerate}

\subsection{Methods}
\begin{enumerate}
\item SendEmail
\item ViewRatingHistory
\item FillFeedback
\item Button AcceptRating
\item Button DeclineRating
\item ScheduleMeeting
\end{enumerate}

\section *{Database}
\subsection{Data members}
\begin{enumerate}
\item Employeename String
\item Managername String
\item Ratinglevel String
\item Feedback String
\item Date date
\end{enumerate}

\subsection{Methods}
\begin{enumerate}
\item AddNewEmployee
\item RemoveEmployee
\item ViewRatingHistory
\item UpdateEmployeeDetails
\end{enumerate}


\end{document}


